Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-08-25 Manuscript/manuscript.tex

\subsection{Comparison of ion binding affinity to experiments by using the electrometer concept} \label{section:electrometer}
Ion binding was compared between experiments and simulations by 
using lipid head group order parameters and ''electrometer concept'' 
introduced by Seelig et al. \cite{seelig87,catte16}.
The concept is based on the experimental observation that the 
order parameters of $\alpha$ and $\beta$ carbons in lipid head group
(see Fig. \ref{??} 
\todo{Figure with chemical structure and labeling to be added}) 
are proportional to the amount of bound charge
in lipid bilayer \cite{seelig87}.
More recent analysis included also
the order parameter signs and concluded that the order parameters  
decrease with bound positive charge and increase with bound negative 
charge \cite{ollila16,catte16}. The observations are rationalized 
as a change of lipid head group dipole tilt to more vertical orientation
with bound positive charge and {\it vice versa} for negative charge \cite{seelig87}. 
Order parameters for $\alpha$ and $\beta$ segments in headgroup, as well as for
all C-H bonds in lipid molecules,
can be accurately measured by using H$^2$ NMR or $^{13}$C NMR techniques.
The experimental order parameters can be compared with the the ones
calculated from MD simulations by using the definition
\begin{equation}\label{OP}
S_{\rm CH}=\frac{3}{2}\langle \cos^2\theta -1 \rangle,
\end{equation}
where $\theta$ is the angle between the bond and membrane
normal and average is taken over all sampled configurations \cite{ollila16}.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=7.0cm]{../Fig/POPCstructure.eps}
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/Order-parameters_exp-L14-ECCL17_q80_sig89.eps}
  \includegraphics[height=8.4cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{simVSexpNOions}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 \cite{dickson14} and ECC-lipids models. 
    Order parameters of head group, glycerol backbone and sn-1 and sn-2 tails  from simulations with Lipid14 \cite{dickson14} and ECC-lipids models
    compared with experimental order parameters from \cite{ferreira13}.}
  \todo{We should run a simulation for the system withtout ions with the
    same (or close) temperature as the experimental data. The NMR data is at 300K
    so that would be good. I think that this would be also close enough for the scattering data at 303K.
  }
\end{figure}

>>>>

\subsection{Comparison of ion binding affinity to experiments by using the electrometer concept} \label{section:electrometer}
Ion binding was compared between experiments and simulations by 
using lipid head group order parameters and ''electrometer concept'' 
introduced by Seelig et al. \cite{seelig87,catte16}.
The concept is based on the experimental observation that the 
order parameters of $\alpha$ and $\beta$ carbons in lipid head group
(see Fig.~\ref{simVSexpNOions}) 
are proportional to the amount of bound charge
in a lipid bilayer \cite{seelig87}.
More recent analysis included also
the order parameter signs and concluded that the order parameters  
decrease with bound positive charge and increase with bound negative 
charge \cite{ollila16,catte16}. The observations are rationalized 
as a change of lipid head group dipole tilt to more vertical orientation
with bound positive charge and {\it vice versa} for negative charge \cite{seelig87}. 
Order parameters for $\alpha$ and $\beta$ segments in headgroup, as well as for
all C-H bonds in lipid molecules,
can be accurately measured by using H$^2$ NMR or $^{13}$C NMR techniques.
The experimental order parameters can be compared with the the ones
calculated from MD simulations by using the definition
\begin{equation}\label{OP}
S_{\rm CH}=\frac{3}{2}\langle \cos^2\theta -1 \rangle,
\end{equation}
where $\theta$ is the angle between the bond and membrane
normal and average is taken over all sampled configurations \cite{ollila16}.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=7.0cm]{../Fig/POPCstructure.eps}
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/Order-parameters_exp-L14-ECCL17_q80_sig89.eps}
  \includegraphics[height=8.4cm,angle=-90]{../Fig/form-f_exp-l14-eccl17.eps}
  \caption{\label{simVSexpNOions}
    X-ray scattering form factors from experiments~\cite{Kucerka2011} and simulations using Lipid14 \cite{dickson14} and ECC-lipids models. 
    Order parameters of head group, glycerol backbone and sn-1 and sn-2 tails  from simulations with Lipid14 \cite{dickson14} and ECC-lipids models
    compared with experimental order parameters from \cite{ferreira13}.}
\end{figure}
